\documentclass[10pt,a4paper]{article}

\usepackage[top=0.45in,bottom=0.45in,left=0.6in,right=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{0.96}

\setlist[itemize]{
  label=-,
  leftmargin=1.2em,
  itemsep=1pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

\titleformat{\section}
  {\normalsize\bfseries}
  {}
  {0pt}
  {}
  [\vspace{-4pt}\rule{\linewidth}{0.4pt}]

\titlespacing{\section}{0pt}{7pt}{2pt}

\newcommand{\resheading}[1]{\section*{#1}}

\newcommand{\resitem}[2]{
  \vspace{2pt}
  \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\
  \end{tabular*}
}

\newcommand{\ressubitem}[1]{
  \textit{#1}\vspace{-2pt}
}

\newcommand{\skillrow}[2]{
  \begin{tabular*}{\textwidth}{@{}p{0.21\textwidth}@{\extracolsep{\fill}}p{0.75\textwidth}@{}}
    \textbf{#1} & #2 \\
  \end{tabular*}
}

\begin{document}

\begin{center}
{\Large \textbf{Gioia Zheng}} \\[2pt]
Rome, Italy \quad | \quad
\href{mailto:gioia.zheng.stud@gmail.com}{gioia.zheng.stud@gmail.com} \quad | \quad
\href{https://www.linkedin.com/in/gioia-zheng-9233a0303}{linkedin.com/in/gioia-zheng-9233a0303} \\[1pt]
\href{https://github.com/GioiaZheng}{github.com/GioiaZheng} \quad | \quad
\href{https://gioiazheng.github.io}{gioiazheng.github.io}
\end{center}

\vspace{-7pt}

\resheading{Profile}
B.Sc. student in Applied Computer Science and Artificial Intelligence at Sapienza University of Rome. Building reproducible retrieval and evaluation systems for large-scale QA pipelines. Interested in research-engineering problems at the intersection of information retrieval, evaluation methodology, and AI infrastructure.

\resheading{Education}
\resitem{Sapienza University of Rome}{Sep 2022 -- Present}
B.Sc. in Applied Computer Science and Artificial Intelligence

\resheading{Projects}

\resitem{MS MARCO Generative QA System}{\href{https://github.com/GioiaZheng/msmarco-genqa}{github.com/GioiaZheng/msmarco-genqa}}
\ressubitem{Python --- Retrieval, Reranking, Generation, Evaluation}
\begin{itemize}
\item Built an end-to-end retrieve $\rightarrow$ rerank $\rightarrow$ generate pipeline on MS MARCO (6,980 queries, 8.8M passages), improving Token-F1 from 0.197 to 0.368.
\item Reproduced sparse, dense, and cross-encoder retrieval stages on CPU-only infrastructure using BM25, SBERT/FAISS, and MiniLM reranking.
\item Built research-engineering infrastructure including CI, config-driven pipelines, experiment manifests, benchmark reporting, optional FastAPI serving, and local / MLflow / W\&B tracking.
\item Analyzed disagreement between lexical and semantic grounding metrics, revealing evaluation inconsistencies in generated QA outputs.
\end{itemize}

\resitem{Handwritten OCR Pipeline}{\href{https://github.com/GioiaZheng/handwritten-ocr-system}{github.com/GioiaZheng/handwritten-ocr-system}}
\ressubitem{PyTorch --- CRNN, BiLSTM, CTC}
\begin{itemize}
\item Designed and trained a CRNN-based handwritten text recognition system combining residual CNN feature extraction, BiLSTM sequence modeling, and CTC decoding.
\item Implemented end-to-end training, evaluation, and monitoring pipelines with CER/WER tracking and TensorBoard instrumentation.
\end{itemize}

\resitem{Chat Service}{\href{https://github.com/GioiaZheng/go-chat-system}{github.com/GioiaZheng/go-chat-system}}
\ressubitem{Go Backend + Vue Frontend + SQLite}
\begin{itemize}
\item Developed a self-contained chat platform with Go backend, Vue frontend, and SQLite persistence packaged as a single deployable artifact.
\item Established automated quality gates including OpenAPI validation, testing, and CI-based build verification.
\end{itemize}

\resheading{Experience}

\resitem{Web Development Intern}{Mar 2026 -- Present}
\ressubitem{Idearia --- Rome, Italy}
\begin{itemize}
\item Developed and maintained PHP / WordPress backend systems for production websites.
\item Built automation workflows using n8n to connect forms, content pipelines, and external services.
\end{itemize}

\resitem{NLP Algorithm Engineer Intern}{Feb 2026 -- May 2026}
\ressubitem{Microsoft --- Natural Language Computing (Remote)}
\begin{itemize}
\item Contributed to retrieval-augmented QA experimentation and evaluation on the MS MARCO benchmark.
\item Built and evaluated retrieval, reranking, generation, and analysis components over a 6,980-query benchmark using BM25, FAISS, sentence-transformers, and T5.
\item Conducted reproducibility, grounding, and failure-analysis studies for RAG pipelines.
\end{itemize}

\resheading{Selected Writing}

\resitem{Retrieval Evaluation Beyond Surface Metrics}{\href{https://gioiazheng.github.io/writing/rag-failure-analysis/}{gioiazheng.github.io/writing/rag-failure-analysis}}
\ressubitem{Technical note --- RAG evaluation, grounding, failure analysis}

\resitem{MS MARCO GenQA Technical Report}{\href{https://gioiazheng.github.io/projects/msmarco-genqa/}{gioiazheng.github.io/projects/msmarco-genqa}}
\ressubitem{Project report --- reproducible retrieval, reranking, and generation}

\resheading{Skills}

\skillrow{Languages}{Python, Go, SQL, JavaScript, PHP}
\skillrow{AI \& Research}{Information Retrieval, RAG Evaluation, PyTorch, FAISS, BM25, Sentence Transformers, Cross-Encoder Reranking}
\skillrow{Web \& Automation}{WordPress, n8n, REST APIs, Vue, OpenAPI}
\skillrow{Systems}{Linux, Docker, GitHub Actions, SQLite}
\skillrow{Spoken Languages}{Chinese (Native), Italian (Bilingual), English (Professional), German (Beginner)}

\end{document}
