% AI-track CV. Concentrates on retrieval / evaluation / RAG-pipeline work.
% A generic-SWE version (with the web-development internship and the
% broader skill list) is intended to be maintained separately from this
% file. Placeholders are marked with \fbox{\textit{TODO: ...}} and must
% be filled in before sending.

\documentclass[10pt,a4paper]{article}

\usepackage[top=0.5in,bottom=0.55in,left=0.6in,right=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}

\setlist[itemize]{itemsep=0pt, topsep=1pt, parsep=0pt, partopsep=0pt, leftmargin=1.2em}

\titleformat{\section}
  {\normalsize\bfseries}
  {}
  {0em}
  {}[\vspace{-4pt}\rule{\linewidth}{0.5pt}]

\titlespacing{\section}{0pt}{4pt}{-3pt}

\linespread{0.93}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ===== helpers =====
\newcommand{\resheading}[1]{\section*{#1}}

\newcommand{\resitem}[2]{
  \vspace{3pt}
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2 \\
  \end{tabular*}
}

\newcommand{\ressubitem}[1]{
  \noindent\textit{#1}\par\vspace{-1pt}
}

\newcommand{\skillrow}[2]{
  \begin{tabular*}{\textwidth}{@{}>{\bfseries}p{0.20\textwidth}@{\extracolsep{\fill}}p{0.76\textwidth}@{}}
    #1 & #2 \\
  \end{tabular*}
}

\newcommand{\todomark}[1]{\fbox{\scriptsize\textbf{TODO}}\,\textit{#1}}

\begin{document}

% ===== Header =====
\begin{center}
    {\Large \textbf{Gioia Zheng}} \\[2pt]
    Rome, Italy \quad | \quad
    \href{mailto:gioia.zheng.stud@gmail.com}{gioia.zheng.stud@gmail.com} \quad | \quad
    \href{https://www.linkedin.com/in/gioia-zheng-9233a0303}{linkedin.com/in/gioia-zheng-9233a0303} \\[1pt]
    \href{https://github.com/GioiaZheng}{github.com/GioiaZheng}
\end{center}

\vspace{-8pt}

% ===== Profile =====
\resheading{Profile}
Undergraduate at Sapienza University of Rome. Building MS MARCO retrieval-augmented QA end-to-end on a single 6-core CPU machine --- BM25, dense (SBERT/FAISS), cross-encoder rerank, T5 generation --- with paired-bootstrap CIs, NLI-entailment grounding, and a regression failure taxonomy. Interested in the gap between surface-form and semantic-faithfulness metrics in RAG evaluation.

% ===== Education =====
\resheading{Education}
\resitem{Sapienza University of Rome}{Sep 2022 -- Present}
B.Sc.\ in Applied Computer Science and Artificial Intelligence
% Coursework intentionally omitted until filled in with real entries — rendering a TODO box is worse than omitting.
% Suggested 4–6 items once available, e.g.: Machine Learning, Information Retrieval, Algorithms, Statistics, Distributed Systems.

% ===== Experience =====
\resheading{Experience}

\resitem{Web Development Intern}{Mar 2026 -- Present}
\ressubitem{Idearia --- Rome, Italy (On-site)}
\begin{itemize}
    \item Developed and maintained PHP / WordPress backend systems for client-facing websites.
    \item Built n8n automation workflows integrating WordPress forms and content with external services, reducing manual operations.
\end{itemize}

\resitem{NLP Algorithm Engineer Intern}{Feb 2026 -- May 2026}
\ressubitem{Microsoft --- Natural Language Computing (Remote)}
\begin{itemize}
    \item Headline result on MS MARCO \texttt{dev/small} (6{,}980 queries, 8.8M-passage corpus): replacing BM25 first-stage with dense top-100 reranked by a cross-encoder, same frozen T5-small generator, lifted Token-F1 \textbf{0.197 $\to$ 0.368} and ROUGE-L \textbf{0.193 $\to$ 0.368}. 95\% paired-bootstrap CIs on per-query $\Delta$ (10k resamples, seed 42) strictly above 0 across all four surface-form metrics.
    \item Pipeline I built and own end-to-end: \texttt{bm25s} sparse (MRR@10 0.170, in line with Anserini's 0.184; gap consistent with tokenizer differences), dense \texttt{all-MiniLM-L6-v2} over a FAISS \texttt{IndexFlatIP} on L2-normalised embeddings, \texttt{cross-encoder/ms-marco-MiniLM-L-6-v2} over the dense top-100 (538k pairs at ${\sim}32$ pairs/s, 4h37m wall-clock on 6 cores), T5-small generation.
    \item Ruled out a surface-form artefact with a DistilBERT-BERTScore proxy on 3{,}000 paired qids: semantic-proxy $\Delta$ \textbf{$+0.173$} sits within 0.002 of the surface-form Token-F1 $\Delta$, well inside encoder noise. Chose DistilBERT over canonical \texttt{roberta-large} as an explicit CPU-cost vs.\ signal tradeoff, documented in the report.
    \item 40-query deterministic-rule triage of the 233-query regression bucket: \textbf{${\sim}$90\% of regressions are generator-side truncation} (mid-word or $\le 3$-token outputs), not retrieval failure. Falsified the decode-budget reading by re-running full \texttt{dev/small} at \texttt{max\_new\_tokens=64$\to$128}: truncation share moved 90\% $\to$ 87.5\%, all four rerank $\Delta$s moved $<0.005$. The output style is intrinsic to T5-small on this prompt format, not a budget symptom.
    \item NLI-entailment grounding (\texttt{cross-encoder/nli-deberta-v3-small}, 3{,}000-pair subsample) is the only metric whose paired $\Delta$ reverses sign: \textbf{$-0.145$} (95\% CI $[-0.16,\,-0.13]$, $p<0.001$). Hypothesis: fragmentary mid-word outputs that inflate token overlap cannot be entailed by a sentence-level NLI cross-encoder. Flagged as a generator-swap follow-up rather than a regression to roll back.
    \item Reproducibility scaffold: per-run manifest (git SHA, config hash, dependency-file hashes, environment fingerprint), pinned \texttt{requirements-lock.txt}, ${\sim}295$-test \texttt{pytest} suite, CI on every push, batch-eval design with no hidden one-shot CLI.
\end{itemize}

% ===== Projects =====
\resheading{Projects}

\resitem{Handwritten OCR pipeline}{\href{https://github.com/GioiaZheng/handwritten-ocr-system}{github.com/GioiaZheng/handwritten-ocr-system}}
\ressubitem{PyTorch --- residual CNN + BiLSTM + CTC, IAM dataset}
\begin{itemize}
    \item CRNN for variable-length handwritten line transcription: 9 residual conv blocks (32$\to$128 channels, batchnorm + leaky-ReLU + dropout 0.2), 2 stacked BiLSTM layers (hidden 256 / 64), linear head over vocab + CTC blank.
    \item Training and held-out evaluation with per-batch CER and WER (\texttt{torchmetrics}) streamed to TensorBoard; greedy CTC decode at inference; preprocessing pipeline (grayscale, normalisation, augmentation).
\end{itemize}

\resitem{LeetCode solutions and pattern notes}{\href{https://github.com/GioiaZheng/Leetcode-Solutions}{github.com/GioiaZheng/Leetcode-Solutions}}
\ressubitem{Python --- schema-validated repo, GitHub Actions CI}
\begin{itemize}
    \item 98 problems, one directory each, with per-problem metadata (id, difficulty, topics, status) validated against a JSON schema. Topic index and catalog regenerated on every push; CI fails if the generated docs drift out of sync with the source metadata.
    \item Quality gate on every push: \texttt{ruff} lint, \texttt{pytest} on a curated subset, structural validation, matrix CI on Python 3.11 and 3.12.
\end{itemize}

\resitem{Chat service}{\href{https://github.com/GioiaZheng/go-chat-system}{github.com/GioiaZheng/go-chat-system}}
\ressubitem{Go backend + Vue frontend + SQLite}
\begin{itemize}
    \item Go REST backend with SQLite for single-writer durability; Vue frontend embedded into the Go binary at build time so the service ships as one static artifact.
    \item OpenAPI schema checked in CI; per-push matrix: \texttt{gofmt}, \texttt{go vet}, unit tests, OpenAPI lint, frontend build.
\end{itemize}

% ===== Open-source / writing =====
% Section intentionally hidden from PDF until at least one verifiable entry exists.
% Strong candidates once available: a methodology write-up on surface-form vs NLI-entailment
% disagreement in RAG evaluation; a HuggingFace dataset card for the MS MARCO genqa outputs;
% an issue or PR against pyserini / ir-measures / BEIR / sentence-transformers / bm25s.
%
% \resheading{Open-source / Writing}
% \vspace{2pt}
% \begin{itemize}
%     \item ...
% \end{itemize}

% ===== Skills =====
\resheading{Skills}
\vspace{2pt}
\skillrow{Primary}{Python, PyTorch, \texttt{bm25s}, FAISS, sentence-transformers, cross-encoder reranking, paired-bootstrap CIs, BERTScore / NLI-entailment grounding, pytest}
\skillrow{Working}{Go, Docker, Linux, GitHub Actions CI, OpenAPI, SQLite, LaTeX}
\skillrow{Familiar}{JavaScript / React Native, Vue}
\skillrow{Languages}{English (Professional), Italian (Bilingual), Chinese (Native), German (Beginner)}

\end{document}
